Meta analysis of reprocessed RNASeq data from AMP-AD for hg38 Reprocessed Data (all 7 brain regions)

### 2020-09-21 code/RNA-Seq_Meta_Analysis.Rmd
Final  Proteomics

# Write results to files
fwrite(meta.anlz.ad_cntrl, file = 'meta.anlz.ad_cntrl.tsv', sep = '\t', row.names = F, quote = F)
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='meta.anlz.ad_cntrl.tsv', name = 'RNASeq AD-Control meta-analysis across 6 brain regions (No CBE) hg38 Reprocessed Data', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
```

>>>>

# Write results to files
fwrite(meta.anlz.ad_cntrl, file = 'RNASeq_meta.anlz.ad_cntrl.tsv', sep = '\t', row.names = F, quote = F)
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='RNASeq_meta.anlz.ad_cntrl.tsv', name = 'RNASeq AD-Control meta-analysis across 6 brain regions (No CBE) hg38 Reprocessed Data', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)

# Write results to files
fwrite(Weights, file = 'RNASeq_meta_weights.ad_cntrl.tsv', sep = '\t', row.names = F, quote = F)
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='RNASeq_meta_weights.ad_cntrl.tsv', name = 'RNASeq AD-Control meta-analysis Weights', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
```
